### 2015-06-25 Projects/DelCo_2012/Report/DelCo_2012.tex
Delco_2012: update to report

\begin{tabbing}
\hspace{1.5in} \= \\
FDS \> Fire Dynamics Simulator \\
HGL \> Hot Gas Layer \\
HRR \> Heat Release Rate \\
HRRPUA \> Heat Release Rate per Unit Area \\
NIST \> National Institute of Standards and Technology \\
\end{tabbing}

@@

\chapter{Abstract}
\label{chap:Abstract}

Traditionally, fire fighting suppression operations have been conducted from the interior of the structure as a means to reduce water damage, manage the “thermal balance,” and limit fire damage to structures.  In current fire fighter training manuals, it is stated that these operations must be coordinated with the ventilation operations.  However guidance on that coordination has been limited.  Previous research and examinations of line of duty deaths have shown that ventilation events occurring with fire fighters in the structure prior to suppression have led to tragic results.  One means of reducing the possibilities of this occurrence would be to begin to extinguish the fire prior to entering the structure.  In effect, an offensive, exterior fire attack, in which water is directed into the structure from the exterior to cool the fire gases and reduce the heat release rate of the fire, prior to the fire fighters entering the building.  The major concern with this type of operation is the potential harm that might occur to people trapped in the structure or the amount of water damage to the structure.  Additionally, the type of suppression agent can affect the fire behavior within the structure.  The suppression agent is the main focus of this study to determine whether or not compressed air foam systems provide any significant benefit to the traditional water application.  Therefore, measurements are needed to document the changes of the thermal environment within the structure due to interior and exterior fire suppression tactics over all types of suppression agents.  This report will focus on water distribution and fire suppression experiments conducted to develop a baseline for the interior fire suppression using both water and compressed air foam application.

\chapter{Introduction}
\label{chap:Introduction}

@@

Three types of experiments were conducted;

1)            spray density measures under non-fire conditions 
2)            gas layer cooling 
3)            fire suppression in an experimental structure

The key measures were to understand the cooling and suppression capabilities of CAFS compared to water.   The experimental designs were developed based on a project planning workshop which included the discussion of incidents where firefighters had concerns or experienced minor burns while using CAFS during interior attack operations in residential occupancies.  [REF-  PROJECT ON “CAPABILITIES AND LIMITATIONS OF COMPRESSED AIR FOAM SYSTEMS (CAFS) FOR STRUCTURAL FIREFIGHTING” WORKSHOP SUMMARY, December, 13-14, 2011.   Casey C. Grant, P.E., Fire Protection Research Foundation, One Batterymarch Park, Quincy, MA USA 02169-7471
17 January 2012]

Since Montgomery County (MD) Fire and Rescue Service provided the CAFS equipped engines and the staffing needed to provide both the water and CAF for the experiments.  Baseline operating conditions were agreed upon at the workshop for these experiments.

*Nozzles – Metro 1, fixed gallonage fog/straight/7/8”solid stream  
100 feet of hose line – 1-3/4”
Foam concentration – 0.3%
CAF Flowrate – 120 gpm / 60 cfm 
Water / air pressure (100-120 psi)

2.3. Study objective
2.3.1. FF exposure – usability / safety
2.3.1.1. Steam blowback
2.3.1.2. Knockdown time
2.3.1.3. Smoke scrubbing
2.3.1.4. Rekindle time / prevention
2.3.1.5. Overhaul / exposure time
2.3.2. Other Issues
2.3.2.1. Structural fire testing
2.3.2.2. Room / attic configuration

These experiments were conducted at the Delaware County Emergency Services Training Center (ESTC) in Sharon Hill, PA.

\chapter{Experimental Setup}
\label{chap:Experimental_Setup}

\section{Experiment Descriptions}
\label{sec:Experiment_Descriptions}

The experimental set-up for this test series is described by the three types of experiments conducted: spray density measures, gas layer cooling, and fire suppression.

\subsection{Spray Density Measures}
\label{sec:Spray_Density_Measures}

Thirty two tests were conducted to determine spray density measures based on various nozzle patterns and locations. The purpose of these tests was to determine the appropriate nozzle locations for the gas cooling and fire suppression tests to follow by gaining an understanding of the water distribution throughout the structures. The gas cooling and fire suppression tests simulated an interior fire attack through the deployment of hose lines inside the structures with fixed nozzles. This set-up is representative of a firefighter operating on a hose line within the structure. Therefore, it is critical to ensure proper nozzle location for the tests to follow to provide the most realistic test conditions.

The nozzles chosen for these experiments were as a result of those available through the MCFRS provided engine and decided upon during the CAFS workshop.  This test series used Task Force Tips (TFT) Metro 1, Fixed Gallonage nozzles with a flow rate of 120 gpm. These are automatic nozzles which have a 7/8 inch slug-tip and can be varied from a straight stream to a wide fog for application. The set-up also included 100 ft of 1-3/4 inch hose.  The nozzles were mounted to a "blitz-fire" monitor device and placed inside the structures.  The nozzles were controlled and operated via a gate valve from the exterior.

The tests conducted for spray density measurement were divided between the available structures at the Delaware County ESTC. Twenty one of the tests were conducted in the concrete burn building where the gas cooling tests would take place, and eleven of the tests were conducted in the experimental structures to be used for the fire suppression tests. The tests varied by changing the nozzle height and location within the structure. Additionally, the nozzle pattern was varied as well. A description and drawings of these facilities can be seen in the Experimental Facility section below.

@@

The experiments were conducted by placing interlocking collector bins across the floor surface area of the burn rooms within each structure. Each collector bin was a 2.5 square foot poly box. The building was sheathed in plastic for the spray density tests in order to protect and preserve as much of the structure as possible before any fire suppression tests were conducted. The nozzles were flowed for a set duration and once the test was concluded, the bins were removed from the structure.  The amount of water in each bin was measured in order to determine how much of the water ended up in each part of the room dependent on the nozzle location and pattern. The results can be seen in the sections to follow.

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Spray_Distribution}
	\caption{Collector Bins and Plastic Sheathing in Experimental Structures}
	\label{fig:Spray_Density_Set_Up}
\end{figure}

\subsection{Gas Cooling}
\label{sec:Gas_Cooling}

The purpose built fire training structure was used for a total of eighty eight experiments studying the effectiveness of cooling the upper gas layer in an adjacent space to the area of fire involvement. The tests were conducted over a period of three days in late September of 2012 and split into a 8 different series. These tests examined five different hose stream patterns through two nozzle types for both compressed air foam and typical water suppression. The area of the purpose built structure used for these experiments was located on the ground floor and involved two adjoining rooms.  The fire was ignited and allowed to grow and fill the compartment with heated fire products and flame.  The developing hot gas layer spread to the adjacent room through a single doorway.  The adjacent room developed a hot gas layer and was the focus of this series of tests.

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCoBurnBuildingSpray}
	\caption{Nozzle Location for Gas Cooling Tests}
	\label{fig:Nozzle_Location_Gas_Cooling_Tests}
\end{figure}

\subsection{Fire Suppression}
\label{sec:Fire_Suppression}

The fire suppression analysis included a series of 14 tests in two single story experimental structures, also located on the grounds of the Delaware County ESTC. Six tests were conducted in the East structure and six tests were conducted in the West structure, each including both water and CAF application as a suppression agent. Additionally, two tests were conducted, one in each structure, on suppression tactics for attic fires in residential dwellings. The nozzle patterns were varied from straight stream to narrow fog, and in the case of the two attic tests, a smooth bore nozzle was used. Several other factors including the fuel load and available ventilation were varied during these tests.

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/burnbuilding}
	\caption{Delaware County, PA Burn Building}
	\label{fig:Delaware_County,_PA_Burn_Building}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Legend2}
	\caption{Instrumentation Legend}
	\label{fig:Instrumentation_Legend}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Single_Story_Instrumentation}
	\caption{Photograph of the Instrumentation in the Fire Suppression Tests.}
	\label{fig:Fire_Suppression_Instrumentation}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/PalletFuelLoad}
	\caption{Pallet Fuel Load}
	\label{fig:Pallet_Fuel_Load}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/SleeperSofa}
	\caption{Sleeper Sofa}
	\label{fig:Sleeper_Sofa}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Mattress}
	\caption{Mattress}
	\label{fig:Mattress}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/BlueChair}
	\caption{Blue Chair}
	\label{fig:Blue_Chair}
\end{figure}

@@

\begin{sidewaystable}[!ht]
	\centering
	\caption{Temperature Comparison}
	\begin{tabular}{ll}
		\hline\noalign{\smallskip}
		Temperature				 & Response		\\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		37 deg C (98.6 deg F)    &  Normal human oral/body temperature      \\
		44 deg C (111 deg F)   	 & Human skin begins to feel pain     \\
		48 deg C (118 deg F) 	 & Human skin receives a first degree burn injury      \\
		55 deg C (131 deg F)     & Human skin receives a second degree burn injury    \\
		62 deg C (140 deg F)     & A phase where burned human tissue becomes numb    \\
		72 deg C (162 deg F)     & Human skin instantly destroyed     \\
		100 deg C (212 deg F)    & Water boils and produces steam    \\
		140 deg C (284 deg F)    & Glass transition temperature of polycarbonate (SCBA Facepieces)      \\
		230 deg C (446 deg F)    & Melting temperature of polycarbonate (SCBA Facepieces)    \\
		250 deg C (482 deg F)    & Charring of natural cotton begins     \\
		>300 deg C (>572 deg F)  & Charring of modern protective clothing fabrics begins    \\
		>600 deg C (>1112 deg F) & Temperatures inside a post-flashover compartment fire     \\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Temperature_Comparison}
\end{sidewaystable}

\begin{sidewaystable}[!ht]
	\centering
	\caption{Heat Flux Comparison}
	\begin{tabular}{ll}
		\hline\noalign{\smallskip}
		Heat Flux	  				   & Response		\\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		1 kW/m\textsuperscript{2}      & Sunny day      \\
		2.5 kW/m\textsuperscript{2}    & Typical firefighter exposure     \\
		3-5 kW/m\textsuperscript{2}    & Pain to skin within seconds      \\
		20 kW/m\textsuperscript{2}     & Threshold flux to floor at flashover onset    \\
		84 kW/m\textsuperscript{2}     & Thermal Protection Performance (TPP) test    \\
		60-200 kW/m\textsuperscript{2} & Flames over surface     \\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Heat_Flux_Comparison}
\end{sidewaystable}

\subsection{Spray Density}
\label{subsec:Spray_Density}

@@

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES1}
	\caption{Experimental Structures Test 1}
	\label{fig:Experimental_Structures_Test_1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES2}
	\caption{Experimental Structures Test 2}
	\label{fig:Experimental_Structures_Test_2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES3}
	\caption{Experimental Structures Test 3}
	\label{fig:Experimental_Structures_Test_3}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES4}
	\caption{Experimental Structures Test 4}
	\label{fig:Experimental_Structures_Test_4}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES5}
	\caption{Experimental Structures Test 5}
	\label{fig:Experimental_Structures_Test_5}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES6}
	\caption{Experimental Structures Test 6}
	\label{fig:Experimental_Structures_Test_6}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES7}
	\caption{Experimental Structures Test 7}
	\label{fig:Experimental_Structures_Test_7}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES72}
	\caption{Experimental Structures Test 7.2}
	\label{fig:Experimental_Structures_Test_7.2}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES8}
	\caption{Experimental Structures Test 8}
	\label{fig:Experimental_Structures_Test_8}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES9}
	\caption{Experimental Structures Test 9}
	\label{fig:Experimental_Structures_Test_9}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES10}
	\caption{Experimental Structures Test 10}
	\label{fig:Experimental_Structures_Test_10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES11}
	\caption{Experimental Structures Test 11}
	\label{fig:Experimental_Structures_Test_11}
\end{figure}

@@

\chapter{Appendix}
\label{chap:Appendix}

\section{Test 1 Figures}
\label{subsec:Test_1_Figures}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Eastside_Array}
	\caption{Test 1 (FSE1): Eastside Array}
	\label{fig:Test_1_Eastside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Westside_Array}
	\caption{Test 1 (FSE1): Westside Array}
	\label{fig:Test_1_Westside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Hallway_Array}
	\caption{Test 1 (FSE1): Hallway Array}
	\label{fig:Test_1_Hallway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Doorway_Array}
	\caption{Test 1 (FSE1): Doorway Array}
	\label{fig:Test_1_Doorway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Eastside_Array}
	\caption{Test 1 (FSE1): Suppression Eastside Array}
	\label{fig:Test_1_Suppression_Eastside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Westside_Array}
	\caption{Test 1 (FSE1): Suppression Westside Array}
	\label{fig:Test_1_Suppression_Westside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Hallway_Array}
	\caption{Test 1 (FSE1): Suppression Hallway Array}
	\label{fig:Test_1_Suppression_Hallway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Doorway_Array}
	\caption{Test 1 (FSE1): Suppression Doorway Array}
	\label{fig:Test_1_Suppression_Doorway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Eastside}
	\caption{Test 1 (FSE1): Eastside Heat Flux}
	\label{fig:Test_1_Eastside_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Westside}
	\caption{Test 1 (FSE1): Westside Heat Flux}
	\label{fig:Test_1_Westside_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Hallway}
	\caption{Test 1 (FSE1): Hallway Heat Flux}
	\label{fig:Test_1_Hallway_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Near_Fire_Room}
	\caption{Test 1 (FSE1): Heat Flux Near Fire Room}
	\label{fig:Test_1_Heat_Flux_Near_Fire_Room}
\end{figure}

\subsection{Velocity}
\label{subsec:Velocity}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Hallway_Velocity}
	\caption{Test 1 (FSE1): Hallway Velocity}
	\label{fig:Test_1_Hallway_Velocity}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Doorway_Velocity}
	\caption{Test 1 (FSE1): Doorway Velocity}
	\label{fig:Test_1_Doorway_Velocity}
\end{figure}

\section{Test 2 Figures}
\label{subsec:Test_2_Figures}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Eastside_Array}
	\caption{Test 2 (FSW2): Eastside Array}
	\label{fig:Test_2_Eastside_Array}
\end{figure}

>>>>

\begin{tabbing}
\hspace{1.5in} \= \\
ESTC \> Delaware County Emergency Services Training Center \\
MCFRS \> Montgomery County (MD) Fire and Rescue Service \\
NIST \> National Institute of Standards and Technology \\
TFT \> Task Force Tips \\
\end{tabbing}

@@

\chapter*{\centering Abstract}
Traditionally, fire fighting suppression operations have been conducted from the interior of the structure as a means to reduce water damage, manage the ``thermal balance'', and limit fire damage to structures. In current fire fighter training manuals, it is stated that these operations must be coordinated with the ventilation operations. However guidance on that coordination has been limited. Previous research and examinations of line of duty deaths have shown that ventilation events occurring with fire fighters in the structure prior to suppression have led to tragic results. One means of reducing the possibilities of this occurrence would be to begin to extinguish the fire prior to entering the structure. In effect, an offensive, exterior fire attack, in which water is directed into the structure from the exterior to cool the fire gases and reduce the heat release rate of the fire, prior to the fire fighters entering the building. The major concern with this type of operation is the potential harm that might occur to people trapped in the structure or the amount of water damage to the structure. Additionally, the type of suppression agent can affect the fire behavior within the structure. The suppression agent is the main focus of this study to determine whether or not compressed air foam systems provide any significant benefit to the traditional water application. Therefore, measurements are needed to document the changes of the thermal environment within the structure due to interior and exterior fire suppression tactics over all types of suppression agents. This report will focus on water distribution and fire suppression experiments conducted to develop a baseline for the interior fire suppression using both water and compressed air foam application.
\pagenumbering{gobble}

\chapter{Introduction}
\label{chap:Introduction}
 \pagenumbering{arabic}
\setcounter{page}{1}

@@

Three types of experiments were conducted: 
\begin{enumerate}
\item spray density measures under non-fire conditions 
\item gas layer cooling 
\item fire suppression in experimental structures
\end{enumerate}

The key measures were to understand the cooling and suppression capabilities of CAFS compared to water. The experimental designs were developed based on a project planning workshop which included the discussion of incidents where firefighters had concerns or experienced minor burns while using CAFS during interior attack operations in residential occupancies~\cite{Grant:2011}.

Since Montgomery County (MD) Fire and Rescue Service (MCFRS) provided the CAFS equipped engines and the staffing needed to provide both the water and CAF for the experiments. Baseline operating conditions were agreed upon at the workshop for these experiments (Table~\ref{tab:op_condition}). These experiments were conducted at the Delaware County Emergency Services Training Center (ESTC) in Sharon Hill, PA.

\begin{table}[!ht]
\centering
\captionof{table}{Operating conditions for experiments}\label{tab:op_condition}
\begin{tabular}{ll}
\toprule[1.5pt]
Equipment    &   Operating Condition \\
\midrule
Nozzle       & Metro 1, fixed gallonage fog,straight, or 7/8~inch solid stream \\
Hoseline     & 100~ft of 1-3/4~inch hoseline \\
Foam         & 0.3\% foam concentration \\
Pressure     & Water and Air pressure of 100 - 120~psi \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

\chapter{Experimental Setup}

\section{Description of Experiments}
\label{sec:desc_experiments}
The experimental setup for this test series is described by the three types of experiments conducted: spray density measures, gas layer cooling, and fire suppression. The nozzles chosen for these experiments were decided upon during the CAFS workshop~\cite{Grant:2011}: Task Force Tips (TFT) Metro 1, fixed gallonage nozzles with a flow rate of 120 gpm. These are automatic nozzles which have a 7/8~inch slug-tip and can be varied from a straight stream to a wide fog for application. The set-up also included 100~ft of 1-3/4~inch hose. Nozzles were mounted to a ``blitz-fire'' monitor device and placed inside the structures. The nozzles were controlled and operated via a gate valve from the exterior.

\subsection{Spray Density}
\label{sec:desc_Spray_Density}

Thirty-two tests were conducted to determine spray density measures based on various nozzle patterns and locations. The gas cooling and fire suppression tests simulated an interior fire attack through the deployment of hose lines inside the structures with fixed nozzles. Therefore, the purpose of these tests was to determine the appropriate nozzle locations for the gas cooling and fire suppression tests to follow by gaining an understanding of the water distribution throughout the structures.

Twenty-one of the tests were conducted in the concrete burn building where the gas cooling tests would take place, and eleven of the tests were conducted in the experimental structures to be used for the fire suppression tests. The test variables were the nozzle height, nozzle location within the test structure, and the nozzle pattern (cf. Fig.~\ref{fig:Spray_Density_Nozzle_Patterns}). A description and drawings of these facilities are included in Section~\ref{sec:Experimental Structures}. Detailed discussion of the tests and results are in Section~\ref{sec:Spray_Density}.

@@

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/Spray_Distribution}
% 	\caption{Collector Bins and Plastic Sheathing in Experimental Structures}
% 	\label{fig:Spray_Density_Set_Up}
% \end{figure}

\subsection{Gas Cooling}
\label{sec:desc_Gas_Cooling}

Eighty-eight experiments were conducted to study the effectiveness of cooling the upper gas layer in a space adjacent to the area of fire involvement. These tests examined five different hose stream patterns, two nozzle types, and both compressed air foam and water as the suppression agent. The focus of this experimental series was to study the impact of the test variables on interior conditions throughout the structure when suppression tactics were applied to a room adjacent to the fire room. Detailed discussion of the tests and results are in Section~\ref{sec:Gas_Cooling}.

\subsection{Fire Suppression}
\label{sec:desc_Fire_Suppression}

The fire suppression series included 14 tests in two single-story experimental structures. Six tests were conducted in the East structure and six tests were conducted in the West structure, each including both water and CAF application as a suppression agent.

Additionally, two tests were conducted, one in each structure, on suppression tactics for attic fires in residential dwellings. The nozzle patterns were varied from straight stream to narrow fog, and in the case of the two attic tests, a smooth bore nozzle was used. Several other factors including the fuel load and available ventilation were varied during these tests.

@@

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/burnbuilding}
% 	\caption{Delaware County, PA Burn Building}
% 	\label{fig:Delaware_County,_PA_Burn_Building}
% \end{figure}

@@

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/Legend2}
% 	\caption{Instrumentation Legend}
% 	\label{fig:Instrumentation_Legend}
% \end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStoryInstrumentation}
	\caption{Photograph of the Instrumentation in the Fire Suppression Tests.}
	\label{fig:Fire_Suppression_Instrumentation}
\end{figure}

@@

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/PalletFuelLoad}
% 	\caption{Pallet Fuel Load}
% 	\label{fig:Pallet_Fuel_Load}
% \end{figure}

@@

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/SleeperSofa}
% 	\caption{Sleeper Sofa}
% 	\label{fig:Sleeper_Sofa}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/Mattress}
% 	\caption{Mattress}
% 	\label{fig:Mattress}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/BlueChair}
% 	\caption{Blue Chair}
% 	\label{fig:Blue_Chair}
% \end{figure}

@@

% \begin{sidewaystable}[!ht]
% 	\centering
% 	\caption{Temperature Comparison}
% 	\begin{tabular}{ll}
% 		\hline\noalign{\smallskip}
% 		Temperature				 & Response		\\
% 		\noalign{\smallskip}\hline\noalign{\smallskip}
% 		37 deg C (98.6 deg F)    &  Normal human oral/body temperature      \\
% 		44 deg C (111 deg F)   	 & Human skin begins to feel pain     \\
% 		48 deg C (118 deg F) 	 & Human skin receives a first degree burn injury      \\
% 		55 deg C (131 deg F)     & Human skin receives a second degree burn injury    \\
% 		62 deg C (140 deg F)     & A phase where burned human tissue becomes numb    \\
% 		72 deg C (162 deg F)     & Human skin instantly destroyed     \\
% 		100 deg C (212 deg F)    & Water boils and produces steam    \\
% 		140 deg C (284 deg F)    & Glass transition temperature of polycarbonate (SCBA Facepieces)      \\
% 		230 deg C (446 deg F)    & Melting temperature of polycarbonate (SCBA Facepieces)    \\
% 		250 deg C (482 deg F)    & Charring of natural cotton begins     \\
% 		>300 deg C (>572 deg F)  & Charring of modern protective clothing fabrics begins    \\
% 		>600 deg C (>1112 deg F) & Temperatures inside a post-flashover compartment fire     \\
% 		\noalign{\smallskip}\hline
% 	\end{tabular}
% 	\label{tab:Temperature_Comparison}
% \end{sidewaystable}

% \begin{sidewaystable}[!ht]
% 	\centering
% 	\caption{Heat Flux Comparison}
% 	\begin{tabular}{ll}
% 		\hline\noalign{\smallskip}
% 		Heat Flux	  				   & Response		\\
% 		\noalign{\smallskip}\hline\noalign{\smallskip}
% 		1 kW/m\textsuperscript{2}      & Sunny day      \\
% 		2.5 kW/m\textsuperscript{2}    & Typical firefighter exposure     \\
% 		3-5 kW/m\textsuperscript{2}    & Pain to skin within seconds      \\
% 		20 kW/m\textsuperscript{2}     & Threshold flux to floor at flashover onset    \\
% 		84 kW/m\textsuperscript{2}     & Thermal Protection Performance (TPP) test    \\
% 		60-200 kW/m\textsuperscript{2} & Flames over surface     \\
% 		\noalign{\smallskip}\hline
% 	\end{tabular}
% 	\label{tab:Heat_Flux_Comparison}
% \end{sidewaystable}

\section{Spray Density}
\label{sec:Spray_Density}

The experiments were conducted by placing 2.5 ft$^2$ interlocking collector bins across the floor surface area of the burn rooms within each structure. The building was sheathed in plastic for the spray density tests to protect and preserve as much of the structure as possible before any fire suppression tests were conducted. Water flowed for a specified duration and upon completion the bins were removed from the structure. Each bin was then weighed to quantify the impact of nozzle location and spray pattern.

@@

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES_1}
	\caption{Experimental Structures Test 1}
	\label{fig:Experimental_Structures_Test_1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES_2}
	\caption{Experimental Structures Test 2}
	\label{fig:Experimental_Structures_Test_2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES_3}
	\caption{Experimental Structures Test 3}
	\label{fig:Experimental_Structures_Test_3}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES_4}
	\caption{Experimental Structures Test 4}
	\label{fig:Experimental_Structures_Test_4}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES_5}
	\caption{Experimental Structures Test 5}
	\label{fig:Experimental_Structures_Test_5}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES_6}
	\caption{Experimental Structures Test 6}
	\label{fig:Experimental_Structures_Test_6}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES_7}
	\caption{Experimental Structures Test 7}
	\label{fig:Experimental_Structures_Test_7}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES_72}
	\caption{Experimental Structures Test 7.2}
	\label{fig:Experimental_Structures_Test_7.2}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES_8}
	\caption{Experimental Structures Test 8}
	\label{fig:Experimental_Structures_Test_8}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES_9}
	\caption{Experimental Structures Test 9}
	\label{fig:Experimental_Structures_Test_9}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES_10}
	\caption{Experimental Structures Test 10}
	\label{fig:Experimental_Structures_Test_10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/ES_11}
	\caption{Experimental Structures Test 11}
	\label{fig:Experimental_Structures_Test_11}
\end{figure}

@@

% \chapter{Appendix}
% \label{chap:Appendix}

% \section{Test 1 Figures}
% \label{subsec:Test_1_Figures}

% \subsection{Temperature}
% \label{subsec:Temperature}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Eastside_Array}
% 	\caption{Test 1 (FSE1): Eastside Array}
% 	\label{fig:Test_1_Eastside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Westside_Array}
% 	\caption{Test 1 (FSE1): Westside Array}
% 	\label{fig:Test_1_Westside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Hallway_Array}
% 	\caption{Test 1 (FSE1): Hallway Array}
% 	\label{fig:Test_1_Hallway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Doorway_Array}
% 	\caption{Test 1 (FSE1): Doorway Array}
% 	\label{fig:Test_1_Doorway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Eastside_Array}
% 	\caption{Test 1 (FSE1): Suppression Eastside Array}
% 	\label{fig:Test_1_Suppression_Eastside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Westside_Array}
% 	\caption{Test 1 (FSE1): Suppression Westside Array}
% 	\label{fig:Test_1_Suppression_Westside_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Hallway_Array}
% 	\caption{Test 1 (FSE1): Suppression Hallway Array}
% 	\label{fig:Test_1_Suppression_Hallway_Array}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Doorway_Array}
% 	\caption{Test 1 (FSE1): Suppression Doorway Array}
% 	\label{fig:Test_1_Suppression_Doorway_Array}
% \end{figure}

% \subsection{Heat Flux}
% \label{subsec:Heat_Flux}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Eastside}
% 	\caption{Test 1 (FSE1): Eastside Heat Flux}
% 	\label{fig:Test_1_Eastside_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Westside}
% 	\caption{Test 1 (FSE1): Westside Heat Flux}
% 	\label{fig:Test_1_Westside_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Hallway}
% 	\caption{Test 1 (FSE1): Hallway Heat Flux}
% 	\label{fig:Test_1_Hallway_Heat_Flux}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Near_Fire_Room}
% 	\caption{Test 1 (FSE1): Heat Flux Near Fire Room}
% 	\label{fig:Test_1_Heat_Flux_Near_Fire_Room}
% \end{figure}

% \subsection{Velocity}
% \label{subsec:Velocity}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Hallway_Velocity}
% 	\caption{Test 1 (FSE1): Hallway Velocity}
% 	\label{fig:Test_1_Hallway_Velocity}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Doorway_Velocity}
% 	\caption{Test 1 (FSE1): Doorway Velocity}
% 	\label{fig:Test_1_Doorway_Velocity}
% \end{figure}

% \clearpage

% \section{Test 2 Figures}
% \label{subsec:Test_2_Figures}

% \subsection{Temperature}
% \label{subsec:Temperature}
